\label{sec:abstract}

% No more than half a page and typically consists of three short paragraphs.
\begin{abstract}

% \begin{mdframed}
% 	\begin{itemize}
% 		\item What the project is about, the principle aims and goals, and specific challenges.
% 		\item How you carried out the project and what work it involved.
% 		\item The results and achievements of the project.
% 	\end{itemize}
% \end{mdframed}

We present a framework for identifying and accelerating the resolution of flaky test cases in a test suite. A flaky test case is one whose outcome is sensitive to some unknown input.

The framework --- \emph{\splatter} --- operates on a continuous lifecycle. To begin, each test's probability of failure is calculated. Then, each test is adaptively instrumented with respect to a budget --- state-logging probes are placed in choice locations. Finally, aggregated data is analysed to identify predicates strongly associated with test failure. At each stage, the framework can work autonomously or with input from a developer.

\todo{
	We present a case study of the Android team and their codebase at Shazam.

	We also formulate some contextual research questions:

	\begin{itemize}
		\item Why are flaky tests a problem?
		\item What are the costs of a flaky test?
	\end{itemize}
}

Our instrumentation approach applies bug isolation techniques in an environment free from previously \todo{enfeebling} characteristics, allowing us to record a richer set of the pieces making up a program's state. We improve probe placement by taking into account control flow graphs, loops and probe cost (overhead).

We discuss and document the implementation of a working proof of concept targeting the Android platform and evaluate its use on tests from the Shazam Android test suite.

\end{abstract}
